Analysis for Biracial Grade Retention Project

### 2022-09-02 analysis/analysis.Rmd
Better labeling on state*year interaction model

sapply(list("categorical, additive"=model_add_cat,
            "categorical, interaction"=model_inter_cat, 
            "continuous, additive"=model_add_cont, 
            "continuous, interaction"=model_inter_cont,
            "add state*year continuous interaction"=model_inter_state),
       BIC) %>%
    enframe("model","BIC") %>%
  kbl() %>%
  kable_styling(full_width=FALSE)

>>>>

sapply(list("categorical, additive"=model_add_cat,
            "categorical, interaction"=model_inter_cat, 
            "continuous, additive"=model_add_cont, 
            "continuous, interaction"=model_inter_cont,
            "continous, interaction + state*year continuous interaction"=model_inter_state),
       BIC) %>%
    enframe("model","BIC") %>%
  kbl() %>%
  kable_styling(full_width=FALSE)
